---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, results = 'hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
 rmarkdown::render("docs/M4_methodology.Rmd", output_format = "github_document")
# file.rename("vignettes/temporal_metabooting.md", "docs/temporal_metabooting.md")
options(knitr.duplicate.label = 'allow')
```

This page contains the explanation of our forecast method for the M4 competition. The description is divided in three sections

 1. [Methodology](docs/M4_methodology.md)
 2. Reproducing the results
 3. Usage example of the package


# M4metalearning

The goal of M4Metalearning is to provide a forecasting metalearning tools, see the example for more information.

## Installation

You can install M4metalearning from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("robjhyndman/M4metalearning",
                         auth_token = "AUTH_TOKEN_REQUIRED_WHILE_REPOSITORY_IS_PRIVATE")
```

You will need and auth token from github, because the repository is private.
See how to create personal tokens here: https://help.github.com/articles/creating-a-personal-access-token-for-the-command-line/

### Note

M4metalearning is using, for the time being, a slight modification of the `tsfeatures` package. Please install it from:

```{r , eval = FALSE}
# install.packages("devtools")
devtools::install_github("pmontman/tsfeatures")
```

Also, a custom version of the `xgboost` package is required. It is installed automatically when calling the training functions that use it, since it does not break compatibility. It just supports customized multiclass objective functions. You may install it manually from:

```{r , eval = FALSE}
# install.packages("devtools")
devtools::install_github("pmontman/customxgboost")
```

# Table of Contents
[Example of metalearning process](#basic_example)

<!-- [Studying metalearning on a temporal crossvalidation dataset](docs/temporal_metabooting.md) -->

##<a name="basic_example"></a> Example

```{r test-main, child = 'vignettes/metalearning_example.Rmd'}
```
